Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-18 paper.tex
[fix] spelling and clarifications

\paragraph{XOR expressiveness}
We did not manage to get Tamarin to terminate for all lemmas and all methods
with the added TEE extension.
%
When the responder uses the \mStat{} authentication method Tamarin did not
complete the in a reasonable time for the authentication lemmas.
%
To combat this, we simplified the modeling of XOR encryption of message\_2 for
these lemmas.
%
More precisely, the second message contains the two values \verb|V| and
\verb|authV|, and we generally model the XOR encryption by xoring each of them
with their own key-stream terms.
%
For the problematic lemmas however, we resorted to xoring the entire tuple
\verb|<V, auth| with single key-stream term.
%
Given that no attacks were identified using our original modeling, this
simplification is intuitively not a severe restriction.
%
However, it is possible that we now miss attacks on these methods 
combining properties of the two-term XOR encryption with TEE capabilities.
%

>>>>

\paragraph{XOR expressiveness}
We did not manage to get Tamarin to terminate for all lemmas and all methods
with the added TEE extension.
%
When the responder uses the \mStat{} authentication method Tamarin did not
complete the in a reasonable time for the authentication lemmas.
%
To combat this, we simplified the modeling of XOR encryption of the second
message for these lemmas when the responder uses \mStat{} authentication.
%
More precisely, the second message contains the two values \verb|V| and
\verb|authV|, and we generally model the XOR encryption by xoring each of them
with their own key-stream terms.
%
For the problematic lemmas however, we resorted to xoring the entire tuple
\verb|<V, auth>| with a single key-stream term.
%
Given that no attacks were identified using our original modeling, this
simplification is intuitively not a severe restriction.
%
However, it is possible that we now miss attacks on these methods
combining properties of the two-term XOR encryption with TEE capabilities.
%
